### 2018-03-08 paper/background.tex
Further work on S2

Another distinguishing feature of \Excel is \emph{self-tracking}. Most build
systems track changes of inputs and intermediate results, executing dependent
tasks whenever they change, but \Excel can also track changes in the tasks
themselves: if a formula was modified, \Excel will recompute it and propagate
the changes. Self-tracking is uncommon in software build systems, where one
often needs to manually initiate a full rebuild even if just a single task has
changed.

@@

\noindent
We first declare the static dependency on \cmd{release.txt}, then read its
content and depend on it, dynamically. Finally, we specify the command line to
produce the resulting archive. Crucially, the archive will only be rebuilt if
one of the dependencies (static or dynamic) has changed.

@@

@@

@@

    \item When build systems are used by large teams, different team members
    often end up executing exactly the same tasks on their local machines.
    A \emph{cloud build system} can speed up builds dramatically by
    transparently sharing build results among team members. Furthermore, cloud
    build systems allow one to perform \emph{shallow builds} that materialise
    only end build products on a local machine, leaving all intermediates in the
    cloud. This is a significant optimisation compared to \emph{deep builds}
    that require all transitive dependencies of an end build product to be
    locally available. Non-cloud build systems cannot support shallow builds.

    \item If a build system executes a task and the result is unchanged from the
    previous build, it is unnecessary to execute the dependent tasks. We call
    this optimisation \emph{early cut-off}. Not all build systems support early
    cut-off: \Make and \Excel do not, whereas \Shake and \Buck do.

@@

\subsection{Dynamic dependencies}

\todo{AM}{Add two examples: include files and cyclic spreadsheet computations.}

>>>>

Another distinguishing feature of \Excel is \emph{self-tracking}. Most build
systems track changes of inputs and intermediate results, executing dependent
tasks whenever they change, but \Excel can also track changes in the tasks
themselves: if a formula is modified, \Excel will recompute it and propagate
the changes. Self-tracking is uncommon in software build systems, where one
often needs to manually initiate a full rebuild even if just a single task has
changed.

@@

\noindent
We first declare the static dependency on \cmd{release.txt}, then read its
content and depend on it, dynamically. Finally, we specify the command to
produce the resulting archive. Crucially, the archive will only be rebuilt if
one of the dependencies (static or dynamic) has changed.

\todo{AM}{How is \Shake different.}

@@

\Shake also supports the following \emph{early cutoff optimisation}. When it
executes a task and the result is unchanged from the previous build, it is
unnecessary to execute the dependent tasks, and hence \Shake can stop a build
earlier, as illustrated in Fig.~\ref{fig-cutoff}. Not all build systems support
early cutoff: \Make and \Excel do not, whereas \Shake and \Bazel (introduced
below) do.

@@

When build systems are used by large teams, different team members
often end up executing exactly the same tasks on their local machines.
A \emph{cloud build system} can speed up builds dramatically by
transparently sharing build results among team members. Furthermore, cloud
build systems allow one to perform \emph{shallow builds} that materialise
only end build products on a local machine, leaving all intermediates in the
cloud. This is a significant optimisation compared to \emph{deep builds}
that require all transitive dependencies of an end build product to be
locally available. Non-cloud build systems cannot support shallow builds.

@@

@@
